Towards a free/open-source universal-dependency treebank for Kazakh

### 2015-06-21 2015-turklang-kazdep/paper.tex
concluding remarks from Fran
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@60937 72bbbca6-d526-0410-a7d9-f06f51895060

\section{Conclusions}\label{sec:conclusions}

>>>>

\section{Concluding remarks}\label{sec:conclusions}

We have presented the first steps towards a free/open-source dependency treebank for
Kazakh with annotation based on the universal dependencies. The treebank is small, but
provides a base for bootstrapping further. Performance of a state-of-the-art statistical
parser trained on the treebank is comparable to other treebanks of similar size.
